Using Fundamental Measure Theory to treat the two-point pair distribution function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-02 papers/pair-correlation/paper.tex
start working on a Matplotlib scons command that will parse python scripts Tested everything on darcy.

%% The homogeneoues limit $g_{sigm}$ can be calculated using the well
%% known and very successful Carnahan Starling equation while the
%% homogeneous limit radial distribution function can be calculated using
%% Monte-Carlo methods.  We used these calculations in a least squares
%% fit along the data points at increasing radial distances in order to
%% fit the perameters of our more general pair correlation function.  Our
%% function will therefore approach the most accurate solution possible
%% in the homogeneous limit.  Created a function that has the form of an
%% expansion in powers of $g_{sigma}$.  $g_{sigm}$ in the homogeneous
%% limit can be calculated using the well known and very successful
%% Carnahan Starling equation.  has a well known and Perameters in the
%% expansion where fit
\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
Figure~\ref{fig:pair-distribution} shows...
\begin{figure}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-0.pdf}
  \includegraphics[width=6cm]{figs/pair-correlation-2-395-5.pdf}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-10.pdf}
  \caption{Plot of the pair distribution function near a hard wall.
    In the interest of space and memeory, we should look at the function and decided which data to add?}\label{fig:pair-distribution}
\end{figure}

>>>>

%% The homogeneoues limit $g_{sigm}$ can be calculated using the well
%% known and very successful Carnahan Starling equation while the
%% homogeneous limit radial distribution function can be calculated using
%% Monte-Carlo methods.  We used these calculations in a least squares
%% fit along the data points at increasing radial distances in order to
%% fit the perameters of our more general pair correlation function.  Our
%% function will therefore approach the most accurate solution possible
%% in the homogeneous limit.  Created a function that has the form of an
%% expansion in powers of $g_{sigma}$.  $g_{sigm}$ in the homogeneous
%% limit can be calculated using the well known and very successful
%% Carnahan Starling equation.  has a well known and Perameters in the
%% expansion where fit
\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
%% Figure~\ref{fig:pair-distribution} shows...
%% \begin{figure}
%%   %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-0.pdf}
%%   \includegraphics[width=6cm]{figs/pair-correlation-2-395-5.pdf}
%%   %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-10.pdf}
%%   \caption{Plot of the pair distribution function near a hard wall.
%%     In the interest of space and memeory, we should look at the function and decided which data to add?}\label{fig:pair-distribution}
%% \end{figure}
